---
title: "Reducing Missed Patient Turns: A Quality Improvement Initiative Through Vocera Phone Alarms"
shorttitle: "Reducing Missed Patient Turns Through Vocera Phone Alarms"
# Set names and affiliations.
# It is nice to specify everyone's orcid, if possible.
# There can be only one corresponding author, but declaring one is optional.
author:
  - name: Michael Avalos Jr  
    corresponding: true
    orcid: 0000-0000-0000-0001
    email: avalosmajr@uchicago.edu
    affiliations:
      - id: id1
        name: "University of Chicago"
        group: Biomedical Sciences Program
        department: Biological Sciences Division
        address: 5841 S. Maryland Ave.
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
  - name: Marianne Banas, RN
    orcid: 0000-0000-0000-0002
    affiliations: 
      - ref: id1
        name: "University of Chicago"
  - name: Peggy Zemansky, RN, BSN, CCRN
    orcid: 0000-0000-0000-0003
    affiliations:
        name: "University of Chicago"
author-note:
  status-changes: 
    affiliation-change: ~
    deceased: ~
  disclosures:
    study-registration: ~
    data-sharing: ~
    related-report: ~
    conflict-of-interest: The authors have no conflicts of interest to disclose.
    financial-support: ~
    gratitude: ~
    authorship-agreements: ~
abstract: "This document is a template demonstrating the apaquarto format."
keywords: [Hospital-acquired pressure injury, Incidence, Intensive care units, Pressure injury, Prevention, Quality Improvement]
# If true, tables and figures are mingled with the text instead of listed at the end of the document.
impact-statement: ~
floatsintext: true
# Numbered lines (.pdf and .docx only)
numbered-lines: false
# File with references
bibliography: bibliography.bib
# Suppress title page
suppress-title-page: false
# Link citations to references
link-citations: true
# Masks references that appear in the masked-citations list
mask: false
masked-citations:
  - schneider2012cattell
  - schneider2015intelligence
# If true, adds today's date below author affiliations. If text, can be any value.
# This is not standard APA format, but it is convenient.
# Works with docx, html, and typst. 
draft-date: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  title-impact-statement: "Impact Statement"
  references-meta-analysis: "References marked with an asterisk indicate studies included in the meta-analysis."
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
    documentmode: jou
    keep-tex: true
---

```{r}
#| label: setup
#| include: false

# Load necessary packages
library(conflicted)
library(tidyverse)
library(papaja)
library(flextable)
library(ftExtra)
library(knitr)
library(broom)

# In addition to strategically ordering your library calls, 
# you can use the conflicts_prefer function to specify which 
# package's function to use when there are multiple options.
conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
conflicts_prefer(flextable::theme_apa, .quiet = TRUE) # we know that we never want the papaja one!

# Set seed
set.seed(1234)

# Generate r-references.bib file (see explanation in the Methods section)
papaja::r_refs(file = "r-references.bib")

```


## Format note: Independent Project Rough Draft should be 3-4 double-spaced pages, excluding the attached bibliography.

## Introduction
  Nurses within intensive care units (ICUs) carry a significant responsibility of ensuring their patient(s) do not develop a hospital-acquired pressure injury (HAPI). Fortunately, current PI prevention approaches do not solely rely on personal knowledge and decision-making but instead guide through skin and risk assessments (e.g., Braden Scale) and repositioning. However, nurses are confronted with countless variables that may affect their performance, including but not limited to heavy workloads, fast-paced environments, and long hours. Collectively, this leads to inadvertent missed turns and documentation, increasing the patient's risk for a HAPI. Therefore, there is a current need to equip nurses better to allow for them to provide the care that they are capable of. The current project aims to reduce missed turns and increase turn documentation within the SICU and BICU through alarms on the nurse's Vocera phones. Characteristics of the intervention includes the alarm being low-priorty, alerting every two hours (totaling six times per shift) and allowing the nurse to choose their own alarm, have the ability to use the snooze feature to si. The primary requirement is that nurses put the alarm into their Vocera phone, which needs to be set at even hours. The effectiveness of the implemented intervention will be analyzed through a comparison of previous patient data within the electronic health records (EHR). This study will help determine whether electronic devices can contribute to a nurse’s provided care and possibly address unforeseen correlations regarding patients and healthcare workers.  

## Research Question
  How effective are the Vocera phone alarms in reminding SICU and BICU nurses to reposition patients and document turns in efforts to prevent hospital-acquired pressure injuries?  

## Literature Review (Approximately 1 page) NEED LIKE 2 MORE SENTENCES 
  For approximately three decades, the Braden Scale has been adopted and served as the primary practice for PI prevention within the United States; nevertheless, PIs remain a concern for hospitals, especially within the intensive care units (ICUs) [@kring2007reliability; @lyder2008pressure; @wei2020predictive]. As technology continues to evolve, it is necessary to utilize even its most simplistic offers, such as alarms, which have shown to be effective in PI prevention. A computer on-screen list, which served as a reminder system, helped the healthcare staff to know the patient’s most recent risk assessment, PI location, and arrival date [@sebastian-viana2016reduction]. The reminder system demonstrated its effectiveness through a reduction of PIs developed [@sebastian-viana2016reduction]. Group A, who was not exposed to the intervention in 2009, reported 84 PIs out of the 9,263 patients, while Group B, who were involved in the reminder system, reported that out of the 9,220 patients, only 59 developed PIs [@sebastian-viana2016reduction]. Moreover, technology in PI prevention consists of various interventions like wearable sensors, which have been classified as “cost-effective”, decrease HAPI development, and improve turn compliance; however, the claim can be made that additional efforts should be made before the purchases of LEAF Sensors at $250/sensor [@crotty2023using]. The Vocera phone alarms may aid in reminding nurses to input turn documentation, turn patients every two hours, and improve patient outcomes through a more cost-effective approach. The intervention shows there is no current need to conduct human subject testing to improve the prevention of PIs; instead, it is necessary to equip nurses better to allow for them to provide the most efficient care.

# NEED TO PUT ONE OF THE CITAITONS AT THE BEGINING TO MEET REQS

## Methods 
### *Data storage*
Weekly audits are performed through chart review and documented on paper. Data collected through audit includes patient initials, room number, MRN, length of stay, Braden Score, turned Q2, description (time of event, type of event, and nurse associated with event), total missed turns, and percentage of turn success for that patients that week. The weekly audit papers remain with Marianne Banas, RN, and Peggy Zemansky, RN, BSN. For this comparison, the data will be transferred from paper and stored within REDCap to ensure the protection of sensitive information. Furthermore, it should be noted that identifiers will be removed. Access to the weekly audit forms includes Michael Avalos Jr., Marianne Banas, RN, and Peggy Zemansky, RN, BSN, CCRN. Access to REDCap will include Michael Avalos Jr. as the primary project owner but may include Marianne Banas, RN, and Peggy Zemansky, RN, BSN, upon request. 

### *EHR data collection*
Data will be extracted from patients before and after the nursing reminders were implemented (7/1/2024 to 5/1/2025). Patients prior to the implementation will undergo the same weekly form measurements as mentioned above; additional variables such as race, gender, age, weight, diseases, and history of pressure injury will be recorded. Information collected from the EHR for patients includes MRN, length of stay, Braden Score, turned Q2, description (time of event, type of event, and nurse associated with event), turn documentation, race, gender, age, weight, diseases, and history of pressure injury. Information collected from the EHR for nurses includes name, shift, experience, and turn documentation. 


## Project Deliverables (Approximately 1/2 page)
 


## Results
  The most committed type of event were missed turns (60) in comparison to repeated turns (40), as seen in @fig-Nurse_Shift_Event. The day and night shift was investigated, which showed consistency amongst both shifts with missed turn being the most common; however, the day shift was associated with 16 more total events than the night shift @fig-Nurse_Shift_Event; furthermore, it was observed that the day 
  
  ---- talking about committing total amount of missed or repeated; however, across all nurses one was less likely to commit a repeated or missed (for example 6 did not commit a certain type). Interesting, the number of events commited by each nurse was relatively similar excepted for nurse ( -------). the nurses that commited the most events were associated with this type of event -----. however the maxium type of event comitted for each nurse was typically --------.  
  
  
The study wanted to investigate whether the type of shift affected either the number and/or type of events commited. it was shown that the day shift committed ---- however for both shifts were popular in the sense that Missed turn was the most committed 


The study wanted to investigate whether events primarily occurred either on weekdays aor weekends (----- check if there is a diff for the type may need to make it). it was shown that the -----  committed ---- however for both shifts were popular in the sense that Missed turn was the most committed 




The study wanted to investigate what was the most common type of event for each age, which show (----- check it for braden scale ). it was shown that the -----  committed ---- however for both shifts were popular in the sense that Missed turn was the most committed 









## Timeline
The timeline displayed below illustrates the plans going forward. 

### **Stage One: Quality Improvement Form** 
- Resubmit quality improvement form by **03/22/25**. 

### **Stage Two: Surverys**
  - Send out surveys to nursing staff by **04/15/25**. 

### **Stage Three: Data Storage**
  - Place all audit data in REDCap by **04/15/25**. 
  - Place all non-intervention data in REDCap by **4/30/25**.
  
### **Stage Four: Observations**
- Observe the intervention in-person (~ 5-10 days) by **05/05/25**.

### **Stage Five: Analysis** 
- Analysis completed by **5/20/25**.

### **Stage Six: Final Write-up**
- Have Final write-up completed by **5/20/25**


## Conclusion (Approximately 1/4 page)
While nurses provide appropriate care, the continuous mental and physical demands allow for an increase in unintentional human error (e.g., missed documentation and turns), reducing efficiency. Therefore, this demonstrates the need to understand the extent to which existing cost-effective tools, such as the Vocera phone alarms, may help improve patient outcomes and nursing performance. Additionally, the project will review the patient’s demographics and health status to understand whether further variables are affecting outcomes


The project aims to reduce missed turns within the SICU and BICU through alarms on the nurse's Vocera phones, reminding them to turn their patient(s) every two hours. The effectiveness of the implemented intervention will be analyzed through a comparison of previous patient data within the EHR.  



Nurses are responsible for ensuring a patient does not develop a pressure injury (PI), which is currently achieved through skin and risk assessments (e.g., Braden Scale) and repositioning. Furthermore, nurses are confronted with countless variables that may affect their performance, including but not limited to heavy workloads, fast-paced environments, and long hours. Collectively, this leads to inadvertent missed documentation and turns, increasing the patient's risk for a PI. 



The intervention has not been proposed to the Alarms Committee at UCM because the alarm itself is not automatic; for instance, alarms that go from the monitor to the staff phone are set alarms. The current intervention may allow the RN to pick their own alarm but requires them to put it into their Vocera phone, which will be set at even hours, alert every two hours, and occur six times per shift. It should be noted that it is not a high-priority alarm, and one may use the snooze feature to si. A decision was made regarding alarm fatigue, which is not classified as a concern here based on the intervention’s collective characteristics of reminding the RN through a phone every two hours (six times per shift), ability to use the snooze feature to si, and not being a high-priority alarm. The current state of the Vocera phone alarms has overwhelmingly increased turn documentation within the SICU and BICU (e.g., 45-50% to 97-98% and no new sacral HAPIs). Nonetheless, questions may arise regarding its effectiveness in the future, such as whether it can become “another alarm,” is reasonable. However, the alarm does carry uniqueness in comparison to others. The alarm obtains a specific known purpose (e.g., turn patient and documentation) and can not be classified or associated as a false alarm. Instead, it is one that alerts at a known set time correlated to a required action. While preventative measures have been implemented and shown to be effective, it is essential not to allow healthcare workers to fall below what is expected of them, regardless of the factors at play. Therefore, the rise in technology use calls for the attempt to dictate whether alarms on Vocera phones may improve missed patient turns, helping to combat the undesired variables nurses face. 




















## References


::: {#refs}
:::






```{r}
#| label: Read_fake_data
# Use readr to read in fake data
fake_data <- read_csv("fake_data.csv")
fake_data

# Write fake_nurse_shift to a .csv file 
getwd()
fake_nurse_shift <- read_csv( "/Users/michaelavalosjr./Repos for Rstudio/Vocera-Phone-Alarms/fake_data.csv")
write_csv(fake_nurse_shift, "fake_nurse_shift.csv")
# Check
fake_nurse_shift



```







```{r} 
#| label: fig-Nurse_Shift_Event
#| fig-cap: "This is the first plot"
ggplot(fake_nurse_shift, aes(x= Shift_Type, fill= `Type of Event`)) +
  geom_bar(position = "stack", width = 0.7, color = "black") +
  geom_text(stat = "count", aes(label = ..count..), 
    position = position_stack(vjust = 0.5), size = 6, color = "white") + # geom_text is labels/text/values for bars here, aes(label = ..count..) is just the count for each category, position _stack places the label inside the bars, vjust helping to center text (vertically remember hjust)
  scale_fill_manual(values = c("Missed Turn" = "blue", "Repeated Turn" = "orange")) +
  labs(title = "Missed and Repeated Turn Occurrence by Shift",
       x = "Shift Type",
       y = "Number of Events",
       fill = "Event Type") +
  theme_minimal(base_family = "Times New Roman") +
  theme(
plot.title = element_text(size = 22, face = "bold", hjust = 0.5),
axis.text.x = element_text(size = 14, face = "bold", color = "black"),
axis.text.y = element_text(size = 12, color = "black"),
axis.title.x = element_text(size = 16, face = "bold"),
axis.title.y = element_text(size = 16, face = "bold"),
legend.position = "top",
legend.title = element_text(size = 14, face = "bold"),
legend.text = element_text(size = 12),
panel.grid.major = element_line(color = "gray90", linetype = "dashed", size = 0.3), 
plot.margin = margin(10, 10, 10, 10),
panel.grid.minor = element_blank())

fake_nurse_shift %>%
  count(`Type of Event`, sort = TRUE) 

fake_nurse_shift
```











